Enabling inference for context-dependent models of mutation by bounding the propagation of dependency

### 2022-03-09 writeups/context-dependence.tex
.

In other applications, reconstruction of an unknown sequence may be of interest.
For instance, training data might be used to estimate parameters of a noisy transmission line,
facilitating the later reconstruction of noisily transmitted signals.
Alternatively, multiple observations of independently transmitted copies of a single sequence
(e.g., down a phylogenetic tree)
might be used to estimate the process, and from this infer the original (ancestral) sequence
(or sample from its posterior distribution).
There is no conceptual barrier to applying these methods to lattices in higher dimensions,
such as noisy images or particle systems used to model other physical processes.
%EM I suggest taking out "used"
However, computational costs will grow with the size of the local neighborhood used
even faster than in one dimension. \revpoint{2}{2}

>>>>

In other applications, reconstruction of an unknown sequence may be of interest.
For instance, training data might be used to estimate parameters of a noisy transmission line,
facilitating the later reconstruction of noisily transmitted signals.
Alternatively, multiple observations of independently transmitted copies of a single sequence
(e.g., down a phylogenetic tree)
might be used to estimate the process, and from this infer the original (ancestral) sequence
(or sample from its posterior distribution).
There is no conceptual barrier to applying these methods to lattices in higher dimensions,
such as noisy images or particle systems modeling other physical processes.
However, computational costs will grow with the size of the local neighborhood used
even faster than in one dimension. \revpoint{2}{2}
